\documentclass[a4paper]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\setlist{nosep}
\raggedright
\input{glyphtounicode}
\pdfgentounicode=1
\usepackage[left=0.4in,top=0.25in,right=0.4in,bottom=0.25in]{geometry}
% \usepackage[scale=0.95]{tgschola}
\usepackage[T1]{fontenc}
\usepackage{titlesec}
\usepackage{array} % Required for boldface (\bf and \bfseries) tabular columns


% ----------- Config ------------

\hypersetup {
    colorlinks   = true, %Colours links instead of ugly boxes
    urlcolor     = blue, %Colour for external hyperlinks
    linkcolor    = blue, %Colour of internal links
}

% ----------- End of Config -----------

% ----------- Definitions -----------
    
\newcommand{\bulletSep} { \vspace{2mm} }

\newcommand{\sectionSep} { \vspace{4mm} }

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-15pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} {
        \large \scshape #1
    }}
    \vspace*{-6pt} \lineunder
    \vspace{1mm}
}

\newcommand{\educationItem}[5]{
    \textbf{#1}\hfill #2\\
    #3, \textit{#4} \hfill #5\\
}

\newcommand{\experienceItem}[5]{
    \textbf{#1} \hfill #2 \\
    \textit{#3} \hfill #4 \\
    \begin{itemize}
        #5
    \end{itemize}
}

\newcommand{\projectItem}[5]{
    {\textbf{#1}} {(\sl #2)}\hfill
    \ifx&#3&%
    % #3 is empty
    \href{#4}{Github}\\
    \else
    % #3 is nonempty
    \href{#3}{Live Preview} | \href{#4}{Github}\\
    \fi
    \begin{itemize}
        #5
    \end{itemize}
}

\newcommand{\activityItem}[3]{
    \textbf{#1} \hfill \textit{#2} \\
    \begin{itemize}
        #3
    \end{itemize}
}


% ----------- End of definitions -----------

\begin{document}

% ----------- Profile -----------

\begin{center}
    {\Huge \scshape \fontfamily{qcs}\selectfont Maharshi Vashistha}\\
    \bulletSep
    LinkedIn: \href{https://www.linkedin.com/in/maharshi-vashistha/}{maharshi-vashistha} $\cdot$
    Github: \href{https://github.com/MaharshiV16}{MaharshiV16} $\cdot$
    Portfolio : \href{https://maharshi.vercel.app/}{maharshi.vercel.app} $\cdot$
    Leetcode: \href{https://leetcode.com/MaharshiV16/}{MaharshiV16} \\
    \bulletSep
    Email: \href {mailto:maharishivashistha@gmail.com}{maharishivashistha@gmail.com} $\cdot$ Mobile: (+91) 63771 13804\\
    \sectionSep
\end{center}

\vspace{-3mm}

% ----------- Education -----------

\header{EDUCATION}

\educationItem{National Institute of Technology, Hamirpur}{Hamirpur}{Bachelor of Technology, Computer Science \& Engineering}{CGPA: 9.09}{Dec 2020 - Present}
% \bulletSep

\sectionSep

% ----------- Work Experience -----------

\header{WORK EXPERIENCE}

\experienceItem{Celebal Technologies}{Hybrid}{Summer Intern}{Jun 2023 - Present}{
     \item Collaborated with the development team, implementing front-end technologies such as ReactJs, Vite, NextJs.
     \item Participated in code reviews and worked closely with senior developers to implement industry best practices, resulting in improved code quality, maintainability, and scalability.
}
\bulletSep

\experienceItem{Indian Institute of Technology Bombay}{Onsite}{Research Intern}{Dec 2022 - Jan 2023}{
     \item Studied 10+ research papers on self-adjusting data structures, with focus on studying and implementing Splay Trees.
     \item Collaborated with professors to understand the foundations and applications of self-adjusting data structures.
}
\bulletSep

\experienceItem{Fly Media Network}{Remote}{ReactJS Intern}{Apr 2022 - Jun 2022}{
     \item Implemented 20+ React components, contributing to the creation of dynamic and responsive web applications.
     \item Collaborated with a cross-functional team of 3 members to deliver high-quality within deadlines.
    \item Actively participated in code reviews, offering feedback and suggestions to enhance code quality and maintainability.
}
\bulletSep

\experienceItem{Alumni Cell Web Team}{Remote}{ReactJS Intern}{Sept 2021 - Oct 2021}{
     \item Contributed to the development of UI components, participated in brainstorming sessions and offered ideas.
    \item Utilized tools such as ReactJs, SASS, Framer Motion, Git, and Github to create scalable front-end solutions.
}

\sectionSep

% ----------- Projects -----------

\header{PROJECTS}

\projectItem{Gapshap}{ReactJs, Firebase, Vite}{https://gapshap.vercel.app/}{https://github.com/MaharshiV16/Gapshap}{
     \item Developed a chat-room application using ReactJS and Firebase, with a focus on creating a simple user interface.
     \item Integrated Firebase Authentication for secure user registration and login functionality, while leveraging Firebase Firestore to enable real-time messaging capabilities.
}\bulletSep

\projectItem{NITH Online Internship Document Signing}{ReactJs, CSS3}{}{https://github.com/MaharshiV16/NITH-Online-Internship-Document-Signing/tree/main}{
     \item Developed key front-end components for the platform, ensuring an intuitive and user-friendly interface.
     \item Followed industry-standard software engineering practices, including version control, code reviews, and agile methodologies, for streamlined development.
}
\sectionSep

% ----------- Skills -----------

\header{SKILLS}
% [t] option means top
\begin{minipage}[t]{0.6\textwidth}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages & C / C++, JavaScript, SQL, HTML, CSS\\
    Technologies and Frameworks & ReactJs, NextJS, Material UI, Git, Firebase, NodeJs, MongoDB, MySQL\\
    Relevant Coursework & Data Structures, Algorithms, DBMS, OOP, Operating Systems,
    \end{tabular}\\
\end{minipage}
\sectionSep

% ----------- Leadership and Activities -----------


\header{LEADERSHIP AND ACTIVITIES}

\activityItem{CSEC NITH}{Coordinator}{
    \item Designed problems and wrote editorials for monthly programming contest \textbf{Heuristics}. 
    \item Conducted programming meets and workshops.
}\bulletSep

\activityItem{GLUG NITH}{Volunteer}{
    \item Organised \textbf{Software Freedom Day} 2022 and promoted FOSS 
    \item Installed various Linux distributions on 50+ systems.
}\bulletSep

\activityItem{Public Relations Club NITH}{Co-Convener}{
    \item Hosted \textbf{Hillffair \& Nimbus} the annual cultural and technical fest respectively.
    \item Worked for campus outreach programs and conducted events such as \textbf{Innovision, Fall Fiesta, March into Spring}. 
    \item Lead a team of 70+ participants for the aforementioned activities.
}
\sectionSep

\end{document}